¿Qué pueden hacer las escuelas para disminuir la desigualdad en el conocimiento cívico?

### 2020-07-31 processing/analysis.Rmd
Corrección análisis
arreglos analisis

# Análisis descriptivo
```{r results='asis'}
summary(data)
stargazer(data, title="Estadísticos descriptivos", type = "html")
hist(data$PV1CIV)
```

@@

datacor<-cor(basecor)
datacor <- corrplot.mixed(datacor)
ggsave(datacor, file = "../output/graphs/graph_cor.png",device = "png",width = 35,height = 25,dpi = "retina",units = "cm")
```

# Análisis multinivel
## Modelo nulo  
```{r}
results_0 = lmer(PV1CIV ~ 1 + (1| idschool), data = data, REML=F)
summary(results_0)
screenreg(results_0) 
```

>>>>

# Análisis descriptivo
```{r}
summary(data)
```

```{r}
hist(data$PV1CIV)
```

@@

datacor<-cor(basecor)
datacor <- corrplot.mixed(datacor)

```

# Análisis multinivel
## Modelo nulo  
```{r results='asis'}
results_0 = lmer(PV1CIV ~ 1 + (1| idschool), data = data, REML=F)
htmlreg(results_0) 
```
